Java Based Memory Latency Simulator

### 2020-11-21 finalPaper/paper.tex
Updated final paper and ref
fixed citations

\subsection{Acquiring Source Code}
To download the simulator code, go to \url{osfinal.dachenhausen.org}
or \url{https://github.com/adamdachenhausen/cs330FinalProject} and clone the repository.
See \url{https:docs.github.com/en/free-pro-team@latest/github/
creating-cloning-and-archiving-repositories/cloning-a-repository} for more.

@@

Rotatational latency of a hard drive is how long does it take a platter to spin, as after all it is a mechanical
component bounded by a certain speed.
According to \cite(1) Eric Shanks from ithollow.com, the following were the Hard Drive Rotational latencies in 2013.

>>>>

\subsection{Acquiring Source Code}
To download the simulator code, go to \url{osfinal.dachenhausen.org}
or \url{https://github.com/adamdachenhausen/cs330FinalProject} and clone the repository.
See
\url{https:docs.github.com/en/free-pro-team@latest/github/creating-cloning-and-archiving-repositories/cloning-a-repository}
for more.

@@

Rotatational latency of a hard drive is how long does it take a platter to spin, as after all it is a mechanical
component bounded by a certain speed.
According to \cite{diskLatency}
